Information Retrieval - Submission Report \\Project N.14: Art For Sale

### 2023-12-11 docs/report/submission.tex
feat: submission report indexer
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

    The \textbf{Information Retrieval System} has capabilities limited to a
    \textbf{TIS} \footnote{Text Information System}
    with \textbf{Text retrieval}.\\
    The \textbf{Text Access} part helping users to retrieve the right information at the right time,
    is structured by connecting the system with users in both modes:
    \begin{itemize}
        \item \textbf{Pull}: user takes initiative to fetch ad-hoc relevant information from the system,
              which offers \textbf{querying} and \textbf{browsing} capabilities.
              It satisfies \textbf{short-term needs}.
        \item \textbf{Push}: system takes initiative and has good knowledge of what are the user's
              \textbf{long-term needs} of information throughout the filtering and recommendation system
              using \textbf{browsing traces} to model the behavior of the user.
    \end{itemize}

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Crawling}\label{sec:crawling}
    It is part of \textbf{Indexing Process}, regarding \textbf{Text Acquisition}, in which the system
    identifies and stores documents for indexing.\\
    The purporse is to harness (relatively) bit text data characterized with the 5
    Vs\footnote{Volume, Variety, Velocity, Value, Veracity}
    located in previous mentioned web sites regarding for sale art.
    Among the 5 Vs, automating the Velocity attribute to keep track of the dynamic real-time data characterizing
    the art selling market was not possible:
    manual re-crawling of the spiders and inverted index re-creation is needed.
    Crawling through Scrapy parses text that is unstructed to group it in well-structured documents,
    allowing them to be easily indexed.
    The structure of each documents is:
    \vspace{-0.2cm}
    \begin{itemize}
        \setlength\itemsep{0.1em}
        \item author
        \item title
        \item price
        \item description
        \item categories
        \item image url reference
        \item post url reference
    \end{itemize}

    The extracted data is subsequently channeled into a \textit{.json} file specified at start.
    After all spiders have been run, every result is manually merged into the \textit{results.json} file.\\
    Our sample volume is around $\approx 8,500$.

    \section{Indexing}\label{sec:indexing}
    It is part of \textbf{Indexing Process},
    regarding \textbf{Text Transformation}, in which the system transforms documents into index terms,
    \textbf{Index Creation}, where index terms are employed to create data structures to support fast searching,
    and \textbf{Ranking and Retrieval}, which uses query and index to generate a ranked list of docs.\\
    The Pyterrier platform supports indexing and retrieval operations by employing shallow
    NLP \footnote{Natural Language Processing}
    techniques.\\
    The indexer served through a FastAPI server in \textit{crawler/index.py} file,
    returns a ranked list of documents in descending order of relevance probability $p \in [0,1]$,
    which is the optimal standard strategy justified by the
    \textbf{Probability Ranking Principle} [Robertson 77].
    The indexer creates the inverted index from the \textit{results.json} file containing the documents.
    \newpage

    Our index.py file uses PyTerrier to create the index starting from the .json file.

    Porter algorithmic Stemmer, stopword list, english word tokenisation is default in pyterrier.

    Around x terms in the \textbf{lexicon}

    BM25 model, similarity-based model with ranked retrieval including TF, IDF and sublinear TF transformation
    to avoid single term dominance.

>>>>

    The \textbf{Information Retrieval System} has capabilities limited to a
    \textbf{TIS}\footnote{Text Information System}
    with \textbf{Text retrieval}.\\
    The \textbf{Text Access} part helping users to retrieve the right information at the right time,
    is structured by connecting the system with users in both modes:
    \begin{itemize}
        \item \textbf{Pull}: user takes initiative to fetch ad-hoc relevant information from the system,
              which offers \textbf{querying} and \textbf{browsing} capabilities.
              It satisfies \textbf{short-term needs}.
        \item \textbf{Push}: system takes initiative and has good knowledge of what are the user's
              \textbf{long-term needs} of information throughout the filtering and recommendation system
              using \textbf{browsing traces} to model the behavior of the user.
    \end{itemize}

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Crawling}\label{sec:crawling}
    It is part of \textbf{Indexing Process}, regarding \textbf{Text Acquisition}, in which the system
    identifies and stores documents for indexing.\\
    The purporse is to harness (relatively) bit text data characterized with the 5
    Vs\footnote{Volume, Variety, Velocity, Value, Veracity}
    located in previous mentioned web sites regarding for sale art.
    Among the 5 Vs, automating the Velocity attribute to keep track of the dynamic real-time data characterizing
    the art selling market was not possible:
    manual re-crawling of the spiders and inverted index re-creation is needed.
    Crawling through Scrapy parses text that is unstructed to group it in well-structured documents,
    allowing them to be easily indexed.
    The structure of each documents is:
    \vspace{-0.1cm}
    \begin{itemize}
        \setlength\itemsep{0.1em}
        \item author
        \item title
        \item price
        \item description
        \item categories
        \item image url reference
        \item post url reference
    \end{itemize}

    The extracted data is subsequently channeled into a \textit{.json} file specified at start.
    After all spiders have been run, every result is manually merged into the \textit{results.json} file.\\
    Our sample volume is around $\approx 8,500$.
    To run crawling refer to project's \textit{README.md}.

    \section{Indexing}\label{sec:indexing}
    It is part of \textbf{Indexing Process},
    regarding \textbf{Text Transformation}, in which the system transforms documents into index terms,
    \textbf{Index Creation}, where index terms are employed to create data structures to support fast searching,
    and \textbf{Ranking and Retrieval}, which uses query and index to generate a ranked list of docs.\\
    The Pyterrier platform supports indexing and retrieval operations by employing shallow
    NLP\footnote{Natural Language Processing}
    techniques.\\
    The indexer served through a FastAPI server in \textit{crawler/index.py} file,
    returns a ranked list of documents in descending order of relevance probability $p \in [0,1]$,
    which is the optimal standard strategy justified by the
    \textbf{Probability Ranking Principle} [Robertson 77].
    The indexer creates the inverted index from the \textit{results.json} file containing the scraped documents.
    Characteristics of index:
    \vspace{-0.1cm}
    \begin{itemize}
        \setlength\itemsep{0.1em}
        \item Stemmer: Porter, algorithmic-basedd, Pyterrier's default
        \item Stopword: Pyterrier's default
        \item Tokenisation: English words, Pyterrier's default
    \end{itemize}

    The retrieval model is BM25: similarity-based model with ranked retrieval including
    TF\footnote{Term Frequency},
    IDF\footnote{Inverse Document Frequency}
    and sublinear TF transformation to avoid single term dominance.
    %Around x terms in the \textbf{lexicon}
    To run the indexer refer to project's \textit{README.md}.
